---
title: "Report"
author: "Weijia Qian"
date: "9/24/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, fig.width = 6, fig.height = 6
)
```

```{r import data}
dat = read.csv("./project1_data-1.csv", header = FALSE, sep = "")
```

```{r data cleaning}
colnames(dat) = c("id", "time", "status", "drug", "age", "sex", "ascites","hepatomegaly", "spiders","edema","serum_bilirubin","serum_cholesterol", "albumin", "urine_copper", "alkaline_phosphatase","SGOT","triglicerides","platelets","prothrombin","histologic_stage")

dat$status = ifelse(dat$status==2,1,0)
dat$bilirubin_cat = ifelse(dat$serum_bilirubin<1.1,1,ifelse(1.1<=dat$serum_bilirubin & dat$serum_bilirubin<=3.3,2,3))
dat$bilirubin_cat = factor(dat$bilirubin_cat, levels=c(1,2,3),labels=c("<1.1","1.1-3.3",">3.3"))
dat$age_year = dat$age/365.25
dat$drug = factor(dat$drug, levels = c(1,2), labels = c("treatment","placebo"))
dat$drug = relevel(dat$drug, ref = 2)
```

### Survival curves
```{r survival plot}
library(survival)
library(survminer)

fit_drug2 <- survfit(Surv(time, status) ~ drug, data = dat)
ggsurvplot(fit_drug2, data=dat, pval=TRUE)
fit_bilirubin2 <- survfit(Surv(time, status) ~ bilirubin_cat, data = dat)
ggsurvplot(fit_bilirubin2, data=dat, pval=TRUE)
```

I used Kepler-Meier estimates to estimate the survival curves by drug and by serum bilirubin level, and then tested whether curves are significantly different by log rank test.  
1. Treatment: $p = 0.75$. There is no significant difference between the survival curves of the treatment and placebo groups.  
2. Serum bilirubin: $p < 0.0001$. There is significant difference between the survival curves of the three serum bilirubin groups.

```{r}
getwd()
devtools::session_info()
```


